Simulating a flock of birds

### 2017-10-29 tex/article.tex
Calculation of eta_c via fit added
some changes in article.tex

If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction. In order to study this behaviour we have determined the average normalized velocity of the system and investigated how it changes when certain parameters are modified:
\begin{equation}
v_a=\frac{1}{Nv}\left\vert\sum_{i=1}^{N} v_i\right\vert
\end{equation}
For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
\todo{refrace}

@@

@@

We further extend the model by implementing a cone-like vision. This means, that rather than averaging the velocities over all birds within a certian radius, we only look at a slice of this circle. For a bird to be within the vision of another bird, it must be within the interaction radius, $r$, and the angle between the birds velocities must be within $\pm \theta_{cone}$. In the limit $\theta_{cone} = 180 \deg$\todo{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.

@@

The alignment, $v_a$, depends on the amount of randomness, $\eta$, in the system and the density, $\rho$, as seen in equations~\eqref{eq:va-eta} and \eqref{eq:va-rho}. In Figure\ref{fig:va_over_eta} we see how, the alignment of the birds decreases as the randomness of their motion increases. The decrease is to be expected as a higher degree of randomness should disrupt alignment. What might be more interesting is the general shape of the curves. We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}. This is also shown in figure~\ref{fig:criticaleta}. The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo{use radians for paper?}. The effects of it will be presented in \ref{subsec:results_conevision}.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\columnwidth]{va_over_eta}
  \caption{Dependance of alignment on randomness}
  \label{fig:va_over_eta}
\end{figure}

@@

We have compared the collective motion of birds to a thermodynamic phase transition. The connection between these is not obvious. However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.

>>>>

If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction. In order to study this behaviour we have determined the average normalized velocity of the system and investigated how it changes when certain parameters are modified:
\begin{equation}
v_a=\frac{1}{Nv}\left\vert\sum_{i=1}^{N} v_i\right\vert
\end{equation}
% Note: here you had a sentence about eta->0 for an unordered and eta->1 for an
% ordered state, this is already explained in more detail in the results and,
% i guess, makes more sense there.

@@

\subsection{Finding $\eta_c$}
To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
\eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
the intersection of the fit curves. Hereby we determine
\begin{align}
\eta_c = 4.56***
\end{align}
\todo{put in final number}

@@

We further extend the model by implementing a cone-like vision. This means, that 
rather than averaging the velocities over all birds within a certian radius, we 
only look at a slice of this circle. For a bird to be within the vision of 
another bird, it must be within the interaction radius, $r$, and the angle 
between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
cone vision and reprocuces the results from \cite{Vicsek}.

@@

The alignment, $v_a$, depends on the amount of randomness $\eta$ in the system 
and the density $\rho$, as seen in equations~\eqref{eq:va-eta} and 
\eqref{eq:va-rho}. In figure~\ref{fig:va_over_eta} we see how the alignment of 
the birds decreases as the randomness of their motion increases. The decrease 
is to be expected, as a higher degree of randomness should disrupt alignment. 
This reflects to $v_a$, which approaches $0$ in a totally unordered state and $1$
in a totally ordered state.
What might be more interesting is the general shape of the curves. We may then 
determine $\beta$ from equation~\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}. 
This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
are all computed without the conevision (equivalent to $\theta_{\text{cone}} = 2\pi$). 
Figure~\ref{fig:va_over_eta} shows how $v_a$ varies with the noise $\eta$ and 
density $\rho$ for a constant value of density and noise respectively.
As it can be seen from the graph the overall alignment of the particles depends 
on the noise and for a high number of particles N the system becomes less ordered. 
For high $\eta$ the flock reaches a coherent moving phase, while for low $\eta$ 
the particles move randomly in the lattice.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\columnwidth]{va_over_eta}
  \caption{Dependence of alignment on randomness}
  \label{fig:va_over_eta}
\end{figure}

@@

We have compared the collective motion of birds to a thermodynamic phase 
transition. However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how more dense systems will display longer effective interaction range.
